On Developing User Interfaces for Piloting Unmanned Systems

### 2014-02-20 Papers/RSN2014/paper.tex
* updated paper text

Imagine a search-and-rescue situation during an earthquake where two large
buildings have collapsed and rescuers need to search the area for survivors. We
highlight such a situation in Figure~\ref{fig:guiding}. Survivors could be located
throughout the affected area (the larger region) but are more likely to be found
in the collapsed building locations, specified as the smaller rectangles. As part
of a simple experiment, we offered a waypoint interface with this overlay, the
sensor range of a small UAV, and asked them to search the entire area with
a preference on the building locations. Each user was allowed to redo their
waypoints after an initial attempt, and we kept track of the number of actions
required, the unexplored areas, and the time required to input the mission.

@@

The usage of the GAMS interface includes the following steps:
\begin{enumerate}
  \item Select the UAS that will be participating with a box or by list of names
  \item Select an action to perform from a list
  \begin{enumerate}
    \item Primitive operations
    \item Network bridging between two locations
    \item Area coverage
    \item Priority area coverage
  \end{enumerate}
  \item Select an area and any subareas necessary for the algorithm
\end{enumerate}

Primitive operations are functions like takeoff, land, move-to-gps, and other
operations that are considered primitive AI. Network bridging is an instruction
to the UAS to move to locations that allow network traffic to pass between
locations. Area coverage is a distributed AI that instructs the UAS to collaborate
in order to cover a single rectangular area. Prioritized area coverage is a distributed AI
that provides for prioritized regions within a main area coverage
that the UAS will try to cover first.

>>>>

Imagine a search-and-rescue situation during an earthquake where two large
buildings have collapsed and rescuers need to search the area for survivors. We
highlight such a situation in Figure~\ref{fig:guiding}. Survivors could be located
throughout the affected area (the larger region) but are more likely to be found
in the collapsed building locations, specified as the smaller rectangles. As part
of a simple experiment, we offered a waypoint interface with this overlay, the
sensor range of a small UAV, and asked users to search the entire area with
a preference on the building locations. Each user was allowed to redo their
waypoints after an initial attempt, and we kept track of the number of actions
required, the unexplored areas, and the time required to input the mission.

@@

The usage of the GAMS interface includes the following steps:
\begin{enumerate}
  \item Select the UAS that will be participating by selecting an area or individual UAS 
  by list of names
  \item Select an action to perform from a list
  \begin{enumerate}
    \item Primitive operations
    \item Network bridging between two locations
    \item Area coverage
    \item Priority area coverage
  \end{enumerate}
  \item Select an area and any subareas necessary for the algorithm
\end{enumerate}

Primitive operations are functions like takeoff, land, move-to-gps, and other
operations that are considered primitive AI. Network bridging is an instruction
to the UAS to move to locations that allow network traffic to pass between
locations. Area coverage is a distributed AI that instructs the UAS to collaborate
in order to cover a single rectangular area. Prioritized area coverage is a distributed AI
that provides for prioritized regions within a main area
that the UAS will try to cover first.
